Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
change to cref

Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
There are 4 binary classifiers, each determines whether a sample belongs to the union of some subclasses marked with boxes, e.g., $d_1$ determines whether a sample belongs to the union of $\{A_{11}, A_{12}, A_{21}, A_{22}\}$.
We can use classifiers $d_1, d_2, d_3$ and set operations for the classification task:
\begin{itemize}
	\item $d_1 - (d_2 + d_3)$ determines samples belong to $A_1$;
	\item $d_1 \cdot d_2 + d_3$ determines samples belong to $A_2$;
	\item $d_2 - d_1$ determines samples belong to $A_3$.
\end{itemize}
For the partial classification task of class $A_3$, it suffices to use only $d_2$ and $d_4$ and their intersection $d_2 \cdot d_4$ to determine samples in $A_3$.

@@

Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

% \linespread{1.1}
\begin{figure}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{fig:assemble-example-encoding}
\end{figure}
% \linespread{1.0}

\subsection{The Heuristic Search Algorithm}
\label{sec:assembly-algorithm}
Based on the encoding method, we propose a search algorithm based on greedy heuristics in Algorithm~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.

\begin{algorithm}[h]
	\caption{The General Algorithm}
	\label{tab:heuristic-search}
	\begin{algorithmic}[1]
		\Require The inputs to the assembly problem;
		\Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
		\Function{Expand}{$D$} \Comment $D$, the classifier set
			\For{$d \in \mathcal{D} - D$}
				\State Calculate the encoding $C$ using $D \cup \{d\}$;
				\State Calculate the entropy $h$ for $C$;
				\State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
			\EndFor
		\EndFunction
		\Function{HeuristicSearch}{}
			\State $\Call{Expand}{\emptyset}$;
			\While{$Q \neq \emptyset$}
				\State $(D, C, h) \gets Pop(Q)$;
				\If{$e_0 == 0$}
					\State \Return $D$;
				\EndIf
				\If{|D| < k}
					\State $\Call{Expand}{D}$;
				\EndIf
			\EndWhile
			\State \Return $\emptyset$;
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\paragraph{Remark.} We do not need to provide the subclasses in the input, because they can be derived from the initial set of classifiers.
Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.

@@

Critical data routing path is extracted through optimizaition of control gates values. We freeze the weights of the model, and for each sample we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values. The gate values can be concatenated into one single vector as representation of that sample. As the original paper \cite{wang2018interpret} states, these gate values encode patterns inside the input images, e.g. tinca in horizontal positions or squat positions will have different encodings.

@@

The visualization of clustering results is presented in figure \ref{fig:vgg-cluster-pca}.

@@

We use methods introduced in paper \cite{LiDongYue} to prune the model according to gate vector of cluster centers (algorithm \ref{alg:prune}).

@@

%\todo{metion CIFAR-5}
\subsection{CDRP Model Assembly}
Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5	\footnote{CIFAR-5 is a shorthand refering to samples having the first 5 class labels in CIFAR-100.} and their relationship to the CDRP clusters by encoding samples using all CDRP models.
Instead of using Venn diagram like the intro example in Figure~\ref{fig:assemble-example-venn}, we use the network diagram in Figure~\ref{fig:network-venn} to represent the relationship between subclasses and clusters.

@@

From Figure~\ref{fig:vgg-cluster}, a cluster from VGG-C typically consists of samples from a single class, which is consistent with the result shown in Figure~\ref{}. 
By contrast, a cluster from VGG-D may contain samples with different labels.

@@

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.

\begin{table}[h]
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline
	\end{tabular}
\end{table}

@@

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers are shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[h]
    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Classifier ID & 3 & 4 & 1 & 2 \\
	\hline
	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\end{tabular}
\end{table}

@@

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}

The corresponding encoding of each class label is shown in Table~\ref{tab:encoding-and-accuarcy}. We can determine the class label with this encoding, the accuracy of which is also shown in Table~\ref{tab:encoding-and-accuarcy}.

\begin{table}[h]
    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 &\\
	\hline
	\end{tabular}
\end{table}

>>>>

\Cref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
There are 4 binary classifiers, each determines whether a sample belongs to the union of some subclasses marked with boxes, e.g., $d_1$ determines whether a sample belongs to the union of $\{A_{11}, A_{12}, A_{21}, A_{22}\}$.
We can use classifiers $d_1, d_2, d_3$ and set operations for the classification task:
\begin{itemize}
	\item $d_1 - (d_2 + d_3)$ determines samples belong to $A_1$;
	\item $d_1 \cdot d_2 + d_3$ determines samples belong to $A_2$;
	\item $d_2 - d_1$ determines samples belong to $A_3$.
\end{itemize}
For the partial classification task of class $A_3$, it suffices to use only $d_2$ and $d_4$ and their intersection $d_2 \cdot d_4$ to determine samples in $A_3$.

@@

\Cref{tab:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in \cref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

% \linespread{1.1}
\begin{table}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{tab:assemble-example-encoding}
\end{table}
% \linespread{1.0}

\subsection{The Heuristic Search Algorithm}
\label{sec:assembly-algorithm}
Based on the encoding method, we propose a search algorithm based on greedy heuristics in \cref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.

\begin{algorithm}
	\caption{The General Algorithm}
	\label{tab:heuristic-search}
	\begin{algorithmic}[1]
		\Require The inputs to the assembly problem;
		\Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
		\Function{Expand}{$D$} \Comment $D$, the classifier set
			\For{$d \in \mathcal{D} - D$}
				\State Calculate the encoding $C$ using $D \cup \{d\}$;
				\State Calculate the entropy $h$ for $C$;
				\State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
			\EndFor
		\EndFunction
		\Function{HeuristicSearch}{}
			\State $\Call{Expand}{\emptyset}$;
			\While{$Q \neq \emptyset$}
				\State $(D, C, h) \gets Pop(Q)$;
				\If{$e_0 == 0$}
					\State \Return $D$;
				\EndIf
				\If{|D| < k}
					\State $\Call{Expand}{D}$;
				\EndIf
			\EndWhile
			\State \Return $\emptyset$;
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\paragraph{Remark.} We do not need to provide the subclasses in the input, because they can be derived from the initial set of classifiers.
Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
For example, in the intro example in \cref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.

@@

Critical data routing path is extracted through optimizaition of control gates values. We freeze the weights of the model, and for each sample we follow the procedure of Distillation Guided Routing (\cref{alg:dgr}) \cite{wang2018interpret} to get the gate values. The gate values can be concatenated into one single vector as representation of that sample. As the original paper \cite{wang2018interpret} states, these gate values encode patterns inside the input images, e.g. tinca in horizontal positions or squat positions will have different encodings.

@@

The visualization of clustering results is presented in \cref{fig:vgg-cluster-pca}.

@@

We use methods introduced in paper \cite{LiDongYue} to prune the model according to gate vector of cluster centers (\cref{alg:prune}).

@@

%\todo{metion CIFAR-5}
\subsection{CDRP Model Assembly}
Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5	\footnote{CIFAR-5 is a shorthand refering to samples having the first 5 class labels in CIFAR-100.} and their relationship to the CDRP clusters by encoding samples using all CDRP models.
Instead of using Venn diagram like the intro example in \cref{fig:assemble-example-venn}, we use the network diagram in \cref{fig:network-venn} to represent the relationship between subclasses and clusters.

@@

From \cref{fig:vgg-cluster}, a cluster from VGG-C typically consists of samples from a single class, which is consistent with the result shown in \cref{fig:vgg-cluster-pca}. 
By contrast, a cluster from VGG-D may contain samples with different labels.

@@

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
From \cref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in \cref{tab:cluster_label}.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline

	\end{tabular}
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
\end{table}

@@

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
\paragraph{Fusion} We implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers. 
Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers are shown in \cref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
	\hline
	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\end{tabular}
    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
\end{table}

@@

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to \cref{tab:cluster_label}

The corresponding encoding of each class label is shown in \cref{tab:encoding-and-accuarcy}. We can determine the class label with this encoding, the accuracy of which is also shown in \cref{tab:encoding-and-accuarcy}.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 &\\
	\hline
	\end{tabular}
    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
\end{table}
